Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit

### 2023-07-04 Manuscript/Manuscript.Rmd
Update by Martin comments

**CRISPR-Cas9 Design and Microinjection**

@@

@@

To identify NOS sequences, we obtained a seed database of oxygenase domains from the Pfam database (PF02898).
From these sequences, we generated a Hidden Markov Model (HMM) to mine the genomes and transcriptomes of 47 metazoan, 2 choanoflagellate and 2 filasterea species.
The HMM model was run in HMMR3 with an e-value of 1e−15.
We ran CD-Hit [@Fu2012] to eliminate redundant sequences (at a 80% threshold).
We aligned the sequences with MAFFT version 7, with the iterative refinement method E-INS-i.
The alignment was trimmed with TrimAl in gappy-out mode [@Capella-Gutierrez2009].
To calculate a maximum-likelihood tree, we used IQ-tree2 with the LG+G4 model.
To calculate branch support, we ran 1000 replicates with the aLRT-SH-like [@Guindon2010] and aBayes methods [@Minh2020].

@@

To identify NIT-GCs, we obtained a seed database of adenylate and guanylate cyclase catalytic domains from the Pfam database (PF00211).
From these sequences, we generated a Hidden Markov Model (HMM) to mine the 45 metazoan, 2 choanoflagellate and 2 filasterea genomes and transcriptomes.
The HMM model was run in HMMR3 [@Eddy2011] with an e-value of 1e−15.
We ran CD-Hit [@Fu2012] to eliminate redundant sequences (at a 80% threshold).
To identify clusters, we used sequence-similarity-based clustering in Clans [@frickey2004] and the convex-clustering option with 100 jack-knife replicates.
The NIT-GCs are extremely well conserved within the membrane-bound guanylate cyclases and form an easily recognizable cluster.
To analyze the phylogeny of NIT-GCs, the cluster containing these GCs together with membrane-bound guanylate cyclases were parsed and used for tree building.
We aligned the sequences with MAFFT version 7, with the iterative refinement method E-INS-i[@Katoh2013].
The alignment was trimmed with TrimAl in gappy-out mode [@Capella-Gutierrez2009].
To calculate a maximum-likelihood tree, we used IQ-tree2 with the LG+G4 model.
To calculate branch support, we ran 1000 replicates with the aLRT-SH-like and aBayes methods [@Minh2020].

>>>>

**CRISPR-Cas9 design and Microinjection**

@@

**Morpholino design**

Morpholino injections were performed as previously described [@Conzelmann2013].
We used the following morpholinos to target the NIT-GC1 and NIT-GC2 genes (GeneTools, LLC).
NIT-GC1 MO1: TGCTTGTCATTATTCAACCAGCAAA, NIT-GC1 MO2: TTCAATTAAACCCTCCAGGTTGCTG, NIT-GC2 MO1: AAATGAAGAGAGGTGTTCTCCTTCG, NIT-GC2 MO2: ATATTCATTATGTGAAGAACTTCCA.

@@

To identify NOS sequences, we obtained a seed database of oxygenase domains from the Pfam database (PF02898).
From these sequences, we generated a Hidden Markov Model (HMM) to mine the genomes and transcriptomes of 47 metazoan, 2 choanoflagellate and 2 filasterea species.
The HMM model was run in HMMR3 [@Eddy2011] with an e-value of 1e−15.
We ran CD-Hit [@Fu2012] to eliminate redundant sequences (at a 80% threshold).
We aligned the sequences with MAFFT version 7, with the iterative refinement method E-INS-i [@Katoh2008].
The alignment was trimmed with TrimAl in gappy-out mode [@Capella-Gutierrez2009].
To calculate a maximum-likelihood tree, we used IQ-tree2 with the LG+G4 model.
To calculate branch support, we ran 1000 replicates with the ultrafast bootstrap approximation (UFBoot) [@Hoang2018] and aLRT-SH-like values [@Guindon2010] methods.

@@

To identify NIT-GCs, we obtained a seed database of adenylate and guanylate cyclase catalytic domains from the Pfam database (PF00211).
From these sequences, we generated a Hidden Markov Model (HMM) to mine the 45 metazoan, 2 choanoflagellate and 2 filasterea genomes and transcriptomes.
The HMM model was run in HMMR3 [@Eddy2011] with an e-value of 1e−15.
We ran CD-Hit [@Fu2012] to eliminate redundant sequences (at a 80% threshold).
To identify clusters, we used sequence-similarity-based clustering in Clans [@frickey2004] and the convex-clustering option with 100 jack-knife replicates.
The NIT-GCs are extremely well conserved within the membrane-bound guanylate cyclases and form an easily recognizable cluster.
To analyze the phylogeny of NIT-GCs, the cluster containing these GCs together with membrane-bound guanylate cyclases were parsed and used for tree building.
We aligned the sequences with MAFFT version 7, with the iterative refinement method E-INS-i [@Katoh2008].
The alignment was trimmed with TrimAl in gappy-out mode [@Capella-Gutierrez2009].
To calculate a maximum-likelihood tree, we used IQ-tree2 with the LG+G4 model.
To calculate branch support, we ran 1000 replicates with the ultrafast bootstrap approximation (UFBoot) [@Hoang2018] and aLRT-SH-like values [@Guindon2010] methods.
